GVN-Hoist: Hoisting Computations from Branches

### 2016-08-19 hoist.tex
load most

@@

\subsection{Comparative analysis of different approaches to hoisting}

>>>>

Loads are hoisted the most followed by scalars, stores and calls in decreasing
order.  This was the common trend in all our experiments. One reason why loads
are hoisted the most is the early execution of this pass (before mem2reg) in the
llvm pass pipeline. Passes like mem2reg, instcombine might actually remove
those loads so this order may change should this pass be scheduled later.

@@

TODO: Table for decrease in the code-size of final binaries.
